% The anatomy of a Nature abstract is annoying, do this later but be aware restrictions allow for 200 words.

%\abstract{The standard cosmological model has proven remarkably successful at describing the evolution of the Universe using only six independent parameters. One of those parameters, $\tau_\reio$ the optical depth to reionization, parametrizes the scatterings that Cosmic Microwave Background photons will experience after decoupling from the primordial plasma as the intergalactic medium eventually transitions from neutral to ionized. The optical depth is a function of neutral hydrogen fraction $x_\HI$ since the photons will scatter off free electrons. However, $x_\HI$ should, in principle, depend on cosmology. Here we show a novel methodology capable of establishing the missing link between cosmology and reionization timeline. We construct a universal shape for the timeline of reionization based on the Gompertz mortality law that maps to any cosmology covered by our simulated data. The mapping between cosmology and reionization is obtained using symbolic regression. Our findings allow us to demote $\tau_\reio$ to derived parameter. Furthermore, we reanalyze CMB data with our universal $x_\HI$ and constrain $\tau_\reio$ to $\approx 1 \%$ and decreases the error on $\As$ by a factor of 2.5 compared to Planck's 2018 data. Although our results depend on the astrophysical assumptions of our simulations, the overall methodology does not, $\tau_\reio$ is after all a function of cosmology.}

\paragraph{\large Abstract}

The standard cosmological model, with its six independent parameters,
has proven remarkably successful in describing the evolution of the
Universe.
One of these parameters, $\tau_\reio$ the optical depth to reionization,
represents the scatterings that Cosmic Microwave Background (CMB)
photons will experience after decoupling from the primordial plasma as
the intergalactic medium transitions from neutral to ionized.
$\tau_\reio$ depends on the neutral hydrogen fraction $x_\HI$, which, in
turn, should theoretically depend on cosmology.
We present a novel method to establish the missing link between
cosmology and reionization timeline.
We discover a\YLtodo{not sure about grammar here} universality in timeline based on the Gompertz mortality
law, applicable to any cosmology within our simulated data. \paulo{Maybe just add  `the' before `timeline'.}
This allows us to construct mapping from cosmology to reionization using
symbolic regression and to treat $\tau_\reio$ as a derived parameter.
Reanalyzing CMB data with our universal $x_\HI$ tightens the constraint
on $\tau_\reio$ by more than one order of magnitude to $\approx 1\%$ and
reduced the error on the amplitude of the primordial fluctuations by a
factor of 2.5 compared to Planck's 2018 constraint.
While our results rely on the astrophysical assumptions in our
simulations, the methodology itself is independent of these assumptions;
after all, $\tau_\reio$ is fundamentally a function of cosmology.
