\paragraph{\large Supplementary information} No.\YLtodo{what's the diff
between this and Extended Data?} \PMCtodo{I think its main purpose is to allow the inclusion of videos and audio files. Also, I think that for social or medical research there would be extra stuff here. }

\paragraph{\large Acknowledgements}
This work is supported by The Major Key project of PCL.
The authors acknowledge PCL's Cloud Brain for providing computational
and data storage resources that have contributed to the results reported
within this paper.

\section*{Declarations}
% If going for Nature astronomy, then we should include here a bunch of required declarations. Most of them will be "NA"...

\paragraph{\large Authors contributions}
P.M.C.\ and Y.L.\ contributed equally to all stages of the project.
M.C.\ contributed to the implementation of the symbolic regression
algorithm.
\paulo{Authors contributed to the manuscript and so on...}

\vspace{-1em}
\paragraph{\large Correspondence and requests for materials}
Should be addressed to Paulo Montero-Camacho and Yin Li.

\vspace{-1em}
\paragraph{\large Code availability}
The paper source files and the scripts used in this work are available
at \href{https://github.com/eelregit/5par}{\faGithub}.

\vspace{-1em}
\paragraph{\large Funding}
Not applicable.

\vspace{-1em}
\paragraph{\large Competing interests}
The authors declare no competing interests.

\vspace{-1em}
\paragraph{\large Ethics approval}
Not applicable.

\vspace{-1em}
\paragraph{\large Consent to participate}
Not applicable.

\vspace{-1em}
\paragraph{\large Consent for publication}
Not applicable.
